Dependent Object Types

### 2012-10-13 doc/fool/article.tex
minor
Template for slides.
Also refactored dot_macros, so that it can be partly used in the
slides.
f-bounded ex

\documentclass[9pt]{sigplanconf}
\input{dot_macros}
\begin{document}

@@

We propose DOT as a core calculus for path-dependent types. We present
the calculus formally in section \ref{dot-calculus} and through
examples in section~\ref{dot-examples}. In
section~\ref{dot-preservation}, we show that the calculus does not
satisfy the standard theorem of preservation, also known as subject
reduction. However, we still believe that the calculus is type-safe,
as discussed in section~\ref{dot-type-safety}. In
section~\ref{discussion}, we discuss choices and variants of the
calculus, as well as related work, and conclude in
section~\ref{conclusion}.

@@

Now, we can create the equivalent of \code{first} ($f$), \code{last}
($l$), \code{recfirst} ($\mi{rf}$) and \code{reclast} ($\mi{rl}$):
\begin{align*}
&\mlnew f {{\mi{m.MetaAlt_c}}\mlldefs{\\
&\gap\gap\mi{choose}(a)=\fun b {\mi{m.MetaAlt_c}} {\mi{m.MetaAlt_c}} a}}{
\mlnew l {{\mi{m.MetaAlt_c}}\mlldefs{\\
&\gap\gap\mi{choose}(a)=\fun b {\mi{m.MetaAlt_c}} {\mi{m.MetaAlt_c}} b}}{
\mlnew {\mi{rf}} {{\mi{m.MetaAlt_c}}\mlldefs{\\
&\gap\gap\mi{choose}(a)=\fun b {\mi{m.MetaAlt_c}} {\mi{m.MetaAlt_c}} {\\
&\gap\gap\gap \app {{\mi{a.choose}}(a)} b}}}{
\mlnew {\mi{rf}} {{\mi{m.MetaAlt_c}}\mlldefs{\\
&\gap\gap\mi{choose}(a)=\fun b {\mi{m.MetaAlt_c}} {\mi{m.MetaAlt_c}} {\\
&\gap\gap\gap \app {{\mi{b.choose}}(a)} b}}}{
}}}}
\end{align*}

>>>>

\documentclass[9pt]{sigplanconf}
\input{macros}
\input{dot_macros}
\begin{document}

@@

We propose DOT as a core calculus for path-dependent types. We present
the calculus formally in section \ref{dot-calculus} and through
examples in section~\ref{dot-examples}. In
section~\ref{dot-preservation}, we show that the calculus does not
satisfy the standard theorem of preservation, also known as subject
reduction. However, we still believe that the calculus is type-safe,
as explained in section~\ref{dot-type-safety}. In
section~\ref{discussion}, we discuss choices and variants of the
calculus, as well as related work, and conclude in
section~\ref{conclusion}.

@@

Now, we can create the equivalent of \code{first} ($f$), \code{last}
($l$), \code{recfirst} ($\mi{rf}$) and \code{reclast} ($\mi{rl}$):
\begin{align*}
&\mlnew f {{\mi{m.MetaAlt_c}}\mlldefs{\\
&\gap\gap\mi{choose}(a)=\fun b {\mi{m.MetaAlt_c}} {\mi{m.MetaAlt_c}} a}}{
\mlnew l {{\mi{m.MetaAlt_c}}\mlldefs{\\
&\gap\gap\mi{choose}(a)=\fun b {\mi{m.MetaAlt_c}} {\mi{m.MetaAlt_c}} b}}{
\mlnew {\mi{rf}} {{\mi{m.MetaAlt_c}}\mlldefs{\\
&\gap\gap\mi{choose}(a)=\fun b {\mi{m.MetaAlt_c}} {\mi{m.MetaAlt_c}} {\\
&\gap\gap\gap \app {{\mi{a.choose}}(a)} b}}}{
\mlnew {\mi{rl}} {{\mi{m.MetaAlt_c}}\mlldefs{\\
&\gap\gap\mi{choose}(a)=\fun b {\mi{m.MetaAlt_c}} {\mi{m.MetaAlt_c}} {\\
&\gap\gap\gap \app {{\mi{b.choose}}(a)} b}}}{
}}}}
\end{align*}
